### 2014-10-22 simulation.Rmd
json-tasep works with Rmd

*Invocation:*
```{r, echo=FALSE}
library(pander)
library(ggplot2)
panderOptions("table.split.table", Inf)  # Let tables become arbitrarily wide rather than wrapping.
source("context-inference-fns.R")
top_n_bottom <- function(df, k) { # Take the top and bottom k rows
    n = nrow(df)
    if(2*k < n) {
        df[c(1:k,(n-(k-1)):n), ]
    }
    else {
        df
    }
}
counts_table <- function(in_longwin, in_shortwin, half_n_show) {
    if ( in_longwin > longwin(model@counts) || in_shortwin > shortwin(model@counts) ) {
        cat("Window size of counts too small.")
    }
    else {
        resids = computeresids(model,
                in_longwin=in_longwin,
                in_shortwin=in_shortwin,
                in_leftwin=in_shortwin,
                counts=model@counts)
        pandoc.table(top_n_bottom(resids, half_n_show), style="rmarkdown")
    }
}
cat(model@invocation)
```

## Details
```{r, echo=FALSE, results="hide"}
# For some reason the code doesn't work if we don't print out some of the
# counts, but we can do it in a hidden block.
counts <- model@counts@counts
head(counts)
```

```{r, echo=FALSE}
cat("left window size:", model@counts@leftwin,
    "\ncomplete window size:", nchar(rownames(counts)[[1]]),
    "\ntotal counts:", sum(counts),
    "\ntime:", simseq.opt$tlen,
    "\nseed:", simseq.opt$seed
    )
```

## Result of fitting operation
```{r, echo=FALSE}
cat("convergence: ", model@results$convergence,
    "\nmessage: ", model@results$message)
```

>>>>

*Invocation:*
```{r, echo=FALSE}
library(pander)
library(ggplot2)
panderOptions("table.split.table", Inf)  # Let tables become arbitrarily wide rather than wrapping.
source("context-inference-fns.R")
top_n_bottom <- function(df, k) { # Take the top and bottom k rows
    n = nrow(df)
    if(2*k < n) {
        df[c(1:k,(n-(k-1)):n), ]
    }
    else {
        df
    }
}
counts_table <- function(in_longwin, in_shortwin, half_n_show) {
    if ( in_longwin > longwin(model@counts) || in_shortwin > shortwin(model@counts) ) {
        cat("Window size of counts too small.")
    }
    else {
        resids = computeresids(model,
                in_longwin=in_longwin,
                in_shortwin=in_shortwin,
                in_leftwin=floor((in_longwin-in_shortwin)/2),
                counts=model@counts)
        pandoc.table(top_n_bottom(resids, half_n_show), style="rmarkdown")
    }
}
cat(model@invocation,"\n")
```

## Details
```{r, echo=FALSE, results="hide"}
# For some reason the code doesn't work if we don't print out some of the
# counts, but we can do it in a hidden block.
counttab <- counts(model)
head(counttab)
```

```{r, echo=FALSE}
cat("left window size:", model@counts@leftwin,
    "\ncomplete window size:", nchar(rownames(counttab)[[1]]),
    "\ntotal counts:", sum(counttab),
    "\ntime:", simseq.opt$tlen,
    "\nseed:", simseq.opt$seed,
    "\n"
    )
```

## Result of fitting operation
```{r, echo=FALSE}
cat("convergence: ", model@results$convergence,
    "\nmessage: ", model@results$message,
    "\n" )
```
